# L&D Library

Welcome to the L&D Library. Here you can find a variety of recommended courses and feedback from your peers. Courses are listed by subject, which can be expanded on by using the plus buttons. If you are looking for a specific course, please click "Open all" and use Ctrl + F to search for it.

If you would like to suggest any courses, resources, or other additions to the L&D Library please contact us: [SET UP EMAIL](). Our aim is to make this library as comprehensive and useful as possible.

```{r, include = FALSE}
library(tidyverse)
library(govdown)

data <- read_csv("Copy of GORS LD Pages Course List Draft 2.csv")
```

::: {.accordion}
## General Analytical Skills
[Reviews: General Analytical Skills](https://airtable.com/shrVIHzn0GHqLIZAD/tblZfSMRzaGsSuODU?filter_Group=General%20Analytical%20Skills) 

```{r, results = 'asis', echo = FALSE}


data_gen <- data %>% filter(Group == "General Analytical Skills") 
for (i in 1:nrow(data_gen)){
  cat(paste0(" \n**",data_gen[i,1],"** "))
   cat(paste0(" \n Type: ",data_gen[i,3]," "))
   cat(paste0(" \n Source: ",data_gen[i,4]," "))
    cat(paste0(" \n Time: ",data_gen[i,5]," "))
  cat(if_else(data_gen[i,6]=="Free"|data_gen[i,6]=="N/A" ,paste0(" \n Cost: ",data_gen[i,6]," "), paste0(" \n Cost: £",data_gen[i,6]," ")))
  cat(paste0(" \n Description: ",data_gen[i,8]," "))
  cat(paste0(" \n Link: ",data_gen[i,7]," \n"))




}
```



## Programming/Data Science
[Reviews: Programming/Data Science](https://airtable.com/shrVIHzn0GHqLIZAD/tblZfSMRzaGsSuODU?filter_Group=Programming/Data%20Science) 

```{r courses_prog , results = 'asis', echo = FALSE}
data_spec <- data %>% filter(Group == "Programming/Data Science") 
for (i in 1:nrow(data_spec)){
    cat(paste0(" \n**",data_spec[i,1],"** "))
   cat(paste0(" \n Type: ",data_spec[i,3]," "))
   cat(paste0(" \n Source: ",data_spec[i,4]," "))
    cat(paste0(" \n Time: ",data_spec[i,5]," "))
  cat(if_else(data_spec[i,6]=="Free"|data_spec[i,6]=="N/A" ,paste0(" \n Cost: ",data_spec[i,6]," "), paste0(" \n Cost: £",data_spec[i,6]," ")))
  cat(paste0(" \n Description: ",data_spec[i,8]," "))
  cat(paste0(" \n Link: ",data_spec[i,7]," \n"))
}


```


## Hard OR
[Reviews: Hard OR courses courses](https://airtable.com/shrVIHzn0GHqLIZAD/tblZfSMRzaGsSuODU?filter_Group=Hard%20OR) 
```{r courses_hard , results = 'asis', echo = FALSE}
data_hard <- data %>% filter(Group == "Hard OR") 
for (i in 1:nrow(data_hard)){
  cat(paste0(" \n**",data_hard[i,1],"** "))
   cat(paste0(" \n Type: ",data_hard[i,3]," "))
   cat(paste0(" \n Source: ",data_hard[i,4]," "))
    cat(paste0(" \n Time: ",data_hard[i,5]," "))
  cat(if_else(data_hard[i,6]=="Free"|data_hard[i,6]=="N/A" ,paste0(" \n Cost: ",data_hard[i,6]," "), paste0(" \n Cost: £",data_hard[i,6]," ")))
  cat(paste0(" \n Description: ",data_hard[i,8]," "))
  cat(paste0(" \n Link: ",data_hard[i,7]," \n"))
}


```


## Soft OR
[Reviews: Soft OR courses](https://airtable.com/shrVIHzn0GHqLIZAD/tblZfSMRzaGsSuODU?filter_Group=Soft%20OR) 

```{r courses_soft , results = 'asis', echo = FALSE}
data_soft <- data %>% filter(Group == "Soft OR") 
for (i in 1:nrow(data_soft)){
    cat(paste0(" \n**",data_soft[i,1],"** "))
   cat(paste0(" \n Type: ",data_soft[i,3]," "))
   cat(paste0(" \n Source: ",data_soft[i,4]," "))
    cat(paste0(" \n Time: ",data_soft[i,5]," "))
  cat(if_else(data_soft[i,6]=="Free"|data_soft[i,6]=="N/A" ,paste0(" \n Cost: ",data_soft[i,6]," "), paste0(" \n Cost: £",data_soft[i,6]," ")))
  cat(paste0(" \n Description: ",data_soft[i,8]," "))
  cat(paste0(" \n Link: ",data_soft[i,7]," \n"))
}

```

[**Systems and complexity**](https://learn.civilservice.gov.uk/courses/btroxfDbQjWETY76YgxRdw) <br>
**Type:** Online <br>
**Source:** Civil Service Learning <br>
**Time:** 3 hours <br>
**Price:** Free <br>
**Description:**  Systems thinking is a problem-solving approach which explores the linkages and interactions between the people, perspectives and other factors present.

## General Professional Skills
[Reviews: General Professional skills courses](https://airtable.com/shrVIHzn0GHqLIZAD/tblZfSMRzaGsSuODU?filter_Group=General%20Professional%20Skills) 

```{r courses_prof , results = 'asis', echo = FALSE}
data_gen_prof <- data %>% filter(Group == "General Professional Skills") 
for (i in 1:nrow(data_gen_prof)){
     cat(paste0(" \n**",data_gen_prof[i,1],"** "))
   cat(paste0(" \n Type: ",data_gen_prof[i,3]," "))
   cat(paste0(" \n Source: ",data_gen_prof[i,4]," "))
    cat(paste0(" \n Time: ",data_gen_prof[i,5]," "))
  cat(if_else(data_gen_prof[i,6]=="Free"|data_gen_prof[i,6]=="N/A"|data_gen_prof[i,6]=="See CSL" ,paste0(" \n Cost: ",data_gen_prof[i,6]," "), paste0(" \n Cost: £",data_gen_prof[i,6]," ")))
  cat(paste0(" \n Description: ",data_gen_prof[i,8]," "))
  cat(paste0(" \n Link: ",data_gen_prof[i,7]," \n"))
}


```


## OR Society
[Reviews: OR Society courses](https://airtable.com/shrVIHzn0GHqLIZAD/tblZfSMRzaGsSuODU?filter_Group=OR%20Society) 


```{r courses_soc , results = 'asis', echo = FALSE}
data_or_soc <- data %>% filter(Group == "OR Society") 
for (i in 1:nrow(data_or_soc)){
     cat(paste0(" \n**",data_or_soc[i,1],"** "))
   cat(paste0(" \n Type: ",data_or_soc[i,3]," "))
   cat(paste0(" \n Source: ",data_or_soc[i,4]," "))
    cat(paste0(" \n Time: ",data_or_soc[i,5]," "))
  cat(if_else(data_or_soc[i,6]=="Free"|data_or_soc[i,6]=="N/A" |data_or_soc[i,6]=="See OR Society" ,
              paste0(" \n Cost: ",data_or_soc[i,6]," "), 
              paste0(" \n Cost: £",data_or_soc[i,6]," ")))
  cat(paste0(" \n Description: ",data_or_soc[i,8]," "))
  cat(paste0(" \n Link: ",data_or_soc[i,7]," \n"))
}


```

## Other GORS Resources
[Reviews: other GORS Resources](https://airtable.com/shrVIHzn0GHqLIZAD/tblZfSMRzaGsSuODU?filter_Group=Other%20GORS%20Resources) 
```{r courses_other , results = 'asis', echo = FALSE}
data_other <- data %>% filter(Group == "Other GORS Resources") 
for (i in 1:nrow(data_other)){
   cat(paste0(" \n**",data_other[i,1],"** "))
   cat(paste0(" \n Type: ",data_other[i,3]," "))
   cat(paste0(" \n Source: ",data_other[i,4]," "))
    cat(paste0(" \n Time: ",data_other[i,5]," "))
  cat(if_else(data_other[i,6]=="Free"|data_other[i,6]=="N/A" |data_other[i,6]=="Refer to framework" ,
              paste0(" \n Cost: ",data_other[i,6]," "), 
              paste0(" \n Cost: £",data_other[i,6]," ")))
  cat(paste0(" \n Description: ",data_other[i,8]," "))
  cat(paste0(" \n Link: ",data_other[i,7]," \n"))
}


```

:::

---

::: {.small-para}
This site was built using

[govdown](https://ukgovdatascience.github.io/govdown/).

:::