# L&D Library

Welcome to the L&D Library. Here you can find a variety of recommended courses and feedback from your peers. Courses are listed by subject, which can be expanded on by using the plus buttons. If you are looking for a specific course, please click "Open all" and use Ctrl + F to search for it.

If you would like to suggest any courses, resources, or other additions to the L&D Library please contact us: [SET UP EMAIL](). Our aim is to make this library as comprehensive and useful as possible.

```{r, include = FALSE}
library(tidyverse)
#library(govdown)

data <- read_csv("Courses/example courses3.csv")
```

::: {.accordion}
## General Analytical Skills

Course reviews: 

```{r, results = 'asis', echo = FALSE}


data_gen <- data %>% filter(category == "general") %>% filter(duplicated(course)==F)
for (i in 1:nrow(data_gen)){
  cat(paste0(" \n**",data_gen[i,1],"** \n"))
  cat(paste0(" \n* ",data_gen[i,5]," \n"))
  cat(paste0(" \n* ",data_gen[i,6]," \n"))
  cat(paste0(" \n* ","More info: ",data_gen[i,7]," \n"))
cat(paste0(" \n","_________ "," \n"))


}
```



## Programming/Data Science
```{r courses_prog , results = 'asis', echo = FALSE}
data_spec <- data %>% filter(category == "Programming/Data Science") %>%filter(duplicated(course)==F)
for (i in 1:nrow(data_spec)){
  cat(paste0(" \n**",data_spec[i,1],"** \n"))
  cat(paste0(" \n* ",data_spec[i,5]," \n"))
  cat(paste0(" \n* ",data_spec[i,6]," \n"))
  cat(paste0(" \n* ","More info: ",data_spec[i,7]," \n"))
cat(paste0(" \n","........."," \n"))
}


```


## Hard OR
```{r courses_hard , results = 'asis', echo = FALSE}
data_hard <- data %>% filter(category == "Hard OR") %>%filter(duplicated(course)==F)
for (i in 1:nrow(data_hard)){
  cat(paste0(" \n**",data_hard[i,1],"** \n"))
  cat(paste0(" \n* ",data_hard[i,5]," \n"))
  cat(paste0(" \n* ",data_hard[i,6]," \n"))
  cat(paste0(" \n* ","More info: ",data_hard[i,7]," \n"))
cat(paste0(" \n","........."," \n"))
}


```


## Soft OR

```{r courses_soft , results = 'asis', echo = FALSE}
data_soft <- data %>% filter(category == "Soft OR") %>%filter(duplicated(course)==F)
for (i in 1:nrow(data_soft)){
  cat(paste0(" \n**",data_soft[i,1],"** \n"))
  cat(paste0(" \n* ",data_soft[i,5]," \n"))
  cat(paste0(" \n* ",data_soft[i,6]," \n"))
  cat(paste0(" \n* ","More info: ",data_soft[i,7]," \n"))
cat(paste0(" \n","........."," \n"))
}


```

[**Systems and complexity**](https://learn.civilservice.gov.uk/courses/btroxfDbQjWETY76YgxRdw) <br>
**Type:** Online <br>
**Source:** Civil Service Learning <br>
**Time:** 3 hours <br>
**Price:** Free <br>
**Description:**  Systems thinking is a problem-solving approach which explores the linkages and interactions between the people, perspectives and other factors present.

## General Professional Skills

[**Influencing skills**](https://learn.civilservice.gov.uk/courses/IEttRlSBQg2c_KxG0Ygu6w) <br>
**Type:** Blended <br>
**Source:** Civil Service Learning <br>
**Time:** 5 hours <br>
**Price:** £229 (ex VAT) <br>
**Description:**  Develop and shape your influencing style to affect your target group - their attitudes, beliefs and behaviours.

[**Presenting confidently**](https://learn.civilservice.gov.uk/courses/ZtVOMjdqQd2ai4IXm-7H4A) <br>
**Type:** Blended <br>
**Source:** Civil Service Learning <br>
**Time:** 3 hours <br>
**Price:** £317 (ex VAT) <br>
**Description:**  Learn the tools and techniques for delivering presentations more effectively and confidently.

[**Conducting high-quality conversations (online)**](https://learn.civilservice.gov.uk/courses/W21M5gwkQNuMLj-Cdb3h4w) <br>
**Type:** Online <br>
**Source:** Civil Service Learning <br>
**Time:** 54 minutes <br>
**Price:** Free <br>
**Description:**  Learn how to open a dialogue effectively and reach the desired constructive outcome.

[**Conducting high-quality conversations**](https://learn.civilservice.gov.uk/courses/pMQn9IGCQwuCbbeqzr8eWw) <br>
**Type:** Blended <br>
**Source:** Civil Service Learning <br>
**Time:** 13 minutes <br>
**Price:** £229 (ex VAT) <br>
**Description:**  This topic helps you understand the emotional triggers that can change the tone of a conversation. During the workshop, you work through some real-life conversations and discover techniques to deal with different situations.

[**Introduction to communicating effectively**](https://learn.civilservice.gov.uk/courses/fM6lUo61QImffsteAxhpaw) <br>
**Type:** Online <br>
**Source:** Civil Service Learning <br>
**Time:** 2 hours 50 minutes <br>
**Price:** Free <br>
**Description:**  Helps customer-facing staff understand the different ways you can communicate with customers and the benefits you gain by using these skills.

[**Introduction to communicating effectively (Blended)**](https://learn.civilservice.gov.uk/courses/pgyb3WeNTDq-kuEJT-vMLg) <br>
**Type:** Online <br>
**Source:** Civil Service Learning <br>
**Time:** 5 hours 35 minutes <br>
**Price:** Free <br>
**Description:**  This awareness-level topic gives you the basics that you need to know to start communicating effectively with your customers.

[**Assertiveness**](https://learn.civilservice.gov.uk/courses/G6YyDvaSSvKVVHDO6sprsQ) <br>
**Type:** Blended <br>
**Source:** Civil Service Learning <br>
**Time:** 3 hours 50 minutes <br>
**Price:** £243 (ex VAT) <br>
**Description:**  This topic is designed to help you discover what assertive behaviour looks like and the skills you can develop to become more assertive.

[**Assertiveness: further resources**](https://learn.civilservice.gov.uk/courses/Kp-5wlwXRp6TWOZWtgsMDA) <br>
**Type:** Online <br>
**Source:** Civil Service Learning <br>
**Time:** 1 hour <br>
**Price:** Free <br>
**Description:**  Freely available resources. Some departments may not allow access to external sites. Civil Service Learning is not responsible for content of external websites.

[**Resilience and wellbeing (online)**](https://learn.civilservice.gov.uk/courses/YzIlqj79RkWUcRzpQriD4A) <br>
**Type:** Online <br>
**Source:** Civil Service Learning <br>
**Time:** 1 hour <br>
**Price:** Free <br>
**Description:**  Understand what resilience means in practice, how you can build it and how to maintain your wellbeing.

:::

---

::: {.small-para}
This site was built using
```{r}
#[govdown](https://ukgovdatascience.github.io/govdown/).
```
:::